Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-04-09 article.tex
Completed 1st part

Transmembrane helices (TMHs) are an overrepresented source of epitopes on major 
histocompatibility complex (MHC) class I for the majority of HLA-I haplotypes. 
It is unknown why there is such a preference exists and 
whether this is the case for MHC-II haplotypes. 
This study shows that also MHC-II binds to polypeptides derived from TMHs 
more often than expected by chance. It is unknown if a signal of
natural selection is present in the proteome coding for TMHs.
This study shows that in the mutation rate in TMHs of [a pathogen] 
are [less/equal/more], hinting at 
evolutionary [conservation/neutrality/disruptive selection].
Our findings suggest that developing vaccines targeting the TMHs of
pathogens is a [good/neutral/bad] idea.

@@

For MHC-1, it was found that epitopes derived from transmembrane helices (TMHs)
are over-presented by all human leukocyte antigen (HLA)-A and 
most HLA-B super types (\cite{bianchi2017}). 
One explanation is that the 
presentation of especially TMHs may have an evolutionary advantage for 
the (human) host. The argumentation for this is that the TMHs are more 
conserved due to the functional requirement of being able to span a lipid 
bilayer. Additionally, there are limited escape mutations possible for the 
pathogen, as many will result in a non-functional TMH.

However, that argumentation can also be countered as there are limited unique 
polypeptide fragments and TMHs are a conserved throughout all species, it is 
likelier that host and pathogen share the same unique epitope sequences, 
resulting in the pathogen avoiding detection due to the negative T-cell 
selection process in the thymus \richel{Frans, jij beweerde dat bacterien
en mensen compleet verschillende TMH sequenties hebben. Als ik dat goed
onthouden hebt, klopt deze paragraaf dus niet}

If presentation of TMH’s on MHC-I would bring an evolutionary advantage 
in the recognition of pathogens by the immune, 
it would follow that this is equally important for MHC-II. 
MHC-II, which is necessary for the activation of B-cells after the detection 
of bacterial pathogens, e.g.  tuberculosis, by dendritic cells or [...]. 
From the earlier research done on MHC-I, it naturally follows to check if 
also MHC-II is more likely to present TMHs than expected by chance. 
Extending the previous study on MHC-I, we also measure the evolutionary 
conservation of TMH epitopes in Mycoplasma pathogens to adress if 
presentation of TMH derived epitopes has an evolutionary advantage.

@@

@@

@@

>>>>

Transmembrane helices (TMHs) in the human proteome
are an overrepresented source of epitopes on major 
histocompatibility complex (MHC) class I for the majority of HLA-I haplotypes. 
This finding may be a methodological artifact and using the proteome
of an actual pathogen nullifies this finding.
Additionally, it is unknown if TMH-II is also likelier to present
TMHs than expected by chance. 
Lastly, if the immune system if more tailored to detect polypeptides
derived from TMHs, can we confirm this by detecting the evolutionary
conservation of this behavior?
This study shows that MHC-I [also has/does not have] more
epitopes derived from a TMH for a pathogen proteome, when compared with
a host proteome.
Additionally, MHC-II binds to polypeptides derived from TMHs 
[less/equally/more] often than expected by chance.
Lastly, this study shows that in the mutation rate in TMHs of a pathogen
is [lower/as much/higher], hinting at 
evolutionary [conservation/neutrality/disruptive selection].
Our findings suggest that the immune system is [less/neutral/more]
vigilant to TMHs than expected by chance and this has left [a/no]
signal in the evolutionary history of the pathogen.

@@

For MHC-1, it was found that epitopes derived 
from human transmembrane helices (TMHs)
are over-presented by all human leukocyte antigen (HLA)-A and 
most HLA-B super types (\cite{bianchi2017}). 
One explanation is that the presentation of TMHs 
may have an evolutionary advantage for 
the (human) host, as TMHs may be more 
conserved due to the functional requirement of being able to span a lipid 
bilayer. 
Due to this, pathogens have a lower chance to develop an escape mutation,
as many mutations will result in a disfunctional TMH.

If presentation of TMHs on MHC-I would bring an evolutionary advantage 
in the recognition of pathogens by the immune, 
it would follow that this is equally important for MHC-II.

If the human immune system is more prone to detect polypeptides
derived from a pathogen's TMHs, one may expect to find an evolutionary
signal in fast-evolving pathogen. 
We can assume that only after the moment that COVID-19 spilled over 
to humans, it's the human immune system that is an influential component 
of its evolutionary selection.
Using the extensive amount of time-dated COVID-19 sequences,
we can quantify to which extent selection in COVID-19 occurs
in the transmembrane part of its proteins.

@@

Figure \ref{fig:1} shows the percentages of epitopes overlapping 
with TMHs for a human and COVID-19 proteome.
The KS test to determine if these percentages are sampled from
a same distribution resulted in a p-value of \richel{unknown},
which makes us reject/accept the hypothesis that these percentages
are sampled from a same distribution.

@@

We found that the percentages of epitopes overlapping 
with TMHs for a human and COVID-19 proteome are 
[similar/different]. In other words, the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its viral pathogen.

@@

We concluded that the
epitopes that MHC-I presents are [as/not as] likely 
to be derived from TMH within either a human host and its viral pathogen.
Because the full COVID-19 only has 4 TMHs \richel{check}, the percentages
of HMC-I epitopes being part of a TMH are likelier to be affected by
stochasticity. We chose to use COVID-19 regardless, as the thousands
of its time-dated genomic sequences are ideal for determining the 
evolutionary conservation of MHC-I detecting TMHs.
